---
title: "final project"
author: "Michael Wagnon"
date: "5/19/2020"
output: html_document
---

```{r}
library(pacman)
p_load(tidyverse,magrittr,dplyr,rdrobust)
```



I think we should do an event study, it seems like the easiest/most sensible option given the data we have. I cleaned up the dataset a little bit and filter to the dates we'd need for an event study. Really we just need to group the different rows into weeks, sum up amount of citations for speeding in each week, create dummy variables for weeks before/after the lockdown order (March 30th) and then run a lil regression. We could also maybe split the types of speeding into normal and crazy (like 100MPH+ or whatever). The Metrics lecture about event studies lays it out pretty nicely. 


```{r}
pacman::p_load(dplyr, tidyverse, lubridate, janitor)
traffic <- read_csv("Traffic_Violations.csv")


#clean column names and filter date into desired timeframe 
traffic_df <- traffic %>%
              clean_names() %>%
              mutate(date_of_stop = as.character(date_of_stop),
                     date_of_stop = mdy(date_of_stop)) %>%
              filter(date_of_stop >= "2020/01/13" & date_of_stop <= "2020/05/18") 

#select necessary columns
traffic_df <- traffic_df %>%
                select(date_of_stop, description, alcohol, race, gender)
             
#filter for speeding citations
speed_df <- filter(traffic_df, grepl('IN EXCESS|EXCEEDING', description)) 

#filter out weird citations for trailers in excess of something
speed_df <- filter(speed_df, !grepl('OPERATE COMBO', description))

#create week bins 
speed_df <- speed_df %>%
              mutate(week_bin = cut(date_of_stop, breaks = "1 week"))

#make variable of count of each week to make things easier

speed_df$week <- speed_df$week_bin 
levels(speed_df$week) <- c(seq(1,18,1))


#count number of speeding citations given in each bin
speed <- speed_df %>%
            group_by(week) %>%
            summarise(speeding = length(description))

#make dummy variables for time periods before and after event
speed <- speed %>%
                mutate(r_neg8 = ifelse(week == "3", 1, 0),
                       r_neg7 = ifelse(week == "4", 1, 0),
                       r_neg6 = ifelse(week == "5", 1, 0),
                       r_neg5 = ifelse(week == "6", 1, 0),
                       r_neg4 = ifelse(week == "7", 1, 0),
                       r_neg3 = ifelse(week == "8", 1, 0),
                       r_neg2 = ifelse(week == "9", 1, 0),
                       r_neg1 = ifelse(week == "10", 1, 0),
                       r_0 = ifelse(week == "11", 1, 0),
                       r_1 = ifelse(week == "12", 1, 0),
                       r_2 = ifelse(week == "13", 1, 0),
                       r_3 = ifelse(week == "14", 1, 0),
                       r_4 = ifelse(week == "15", 1, 0),
                       r_5 = ifelse(week == "16", 1, 0),
                       r_6 = ifelse(week == "17", 1, 0),
                       r_7 = ifelse(week == "18", 1, 0),
                       r_not = ifelse(week == "1" | week == "2", 1, 0))

#run event study regression

speed_lm <- lm(speeding ~ r_neg8 + r_neg7 + r_neg6 + r_neg5 + r_neg4 + r_neg3 + r_neg2 + r_neg1 + 
                    r_0 + r_1 + r_2 + r_3 + r_4 + r_5 + r_6 + r_7, data = speed)

summary(speed_lm)


#COOL NOTHING IS SIGNIFICANT AND I ALSO DON'T KNOW IF I DID IT RIGHT
```