---
title: "Event Study"
author: "Michael Wagnon"
date: "6/1/2020"
output: html_document
---
```{r}
#Load packages
library(pacman)
p_load(tidyverse,magrittr,dplyr,rdrobust,lubridate,janitor,huxtable,stringr)

#Load the dataset
traffic_df <- read.csv("multiyear.csv") %>%
              clean_names()

#select necessary columns and convert date to date
traffic_df %<>% 
  mutate(date_of_stop = mdy(date_of_stop))

#make separate variable for just year 
traffic_df$year <- year(traffic_df$date_of_stop)

#make variable that gives us day of the year
traffic_df$day <- yday(traffic_df$date_of_stop)

#group days into weeks
traffic_df <- traffic_df %>%
              mutate(week = floor(day/7)+1)

#Create a count of violations by year and week
traffic_df$violation <- 1

vio_df <- traffic_df %>%
  group_by(year, week) %>%
  summarise(violations = sum(violation))

#Create a date variable for the starting date of each week
vio_df %<>%
  mutate(week_start = weeks(week-1) + ymd(str_c(year, "-01-01")))

#Create an indicator for policy

vio_df$sip <- ifelse(vio_df$week_start >= as.Date("2020-03-12")-days(3), 1, 0)

#create an indicator for whether it is the year of covid-19
vio_df$cov <- ifelse(vio_df$year == "2020", 1, 0)

#create indicator for all years for the policy
vio_df$sip_all <- ifelse(vio_df$week >= 11, 1, 0)
```

Here I run an event study regression like the one covered in the Metrics lecture. It shows the week that most business were closed down, and gatherings of 50+ were prohibited as significant where no other week is, but I'm not sure about the interpretation of it.
```{r}
#create dummies for the 8 weeks on either side of the Covid-19 policy change
vio_df %<>%
  mutate(r_neg8 = ifelse(week == 2 & year == 2020, 1, 0),
         r_neg7 = ifelse(week == 3 & year == 2020, 1, 0),
         r_neg6 = ifelse(week == 4 & year == 2020, 1, 0),
         r_neg5 = ifelse(week == 5 & year == 2020, 1, 0),
         r_neg4 = ifelse(week == 6 & year == 2020, 1, 0),
         r_neg3 = ifelse(week == 7 & year == 2020, 1, 0),
         r_neg2 = ifelse(week == 8 & year == 2020, 1, 0),
         r_neg1 = ifelse(week == 9 & year == 2020, 1, 0),
         r_0 = ifelse(week == 11 & year == 2020, 1, 0),
         r_1 = ifelse(week == 12 & year == 2020, 1, 0),
         r_2 = ifelse(week == 13 & year == 2020, 1, 0),
         r_3 = ifelse(week == 14 & year == 2020, 1, 0),
         r_4 = ifelse(week == 15 & year == 2020, 1, 0),
         r_5 = ifelse(week == 16 & year == 2020, 1, 0),
         r_6 = ifelse(week == 17 & year == 2020, 1, 0),
         r_7 = ifelse(week == 18 & year == 2020, 1, 0),
         r_8 = ifelse(week == 19 & year == 2020, 1, 0),
         r_9 = ifelse(week == 20 & year == 2020, 1, 0),
         r_10 = ifelse(week == 21 & year == 2020, 1, 0),
         r_not = ifelse(week == 1 | week >= 18 & year ==2020, 1,
                        ifelse(year != 2020, 1, 0)))

#run event study regression
speed_lm <- lm(violations ~ r_neg8 + r_neg7 + r_neg6 + r_neg5 + r_neg4 + r_neg3 + r_neg2 + r_neg1 + 
                    r_0 + r_1 + r_2 + r_3 + r_4 + r_5 + r_6 + r_7 + r_8 + r_9 + r_10, data = vio_df)

huxreg(speed_lm)


for_graph <- speed_lm$coefficients %>% as.data.frame()
for_graph$variable <- rownames(for_graph)
rownames(for_graph) <- 0:19
for_graph$week <- rownames(for_graph)
for_graph %<>% select(c(week,.)) %>% mutate(week = as.numeric(week))

for_graph %>% ggplot(aes(x=week,y=.)) +
  geom_point()
```

Here is a super basic regression that will work if we really need it. 
```{r}
#run a rudimentary regression
did_lm <- lm(violations ~ cov + sip_all + sip_all:cov, data = vio_df)

huxreg(did_lm)
```


```{r}
p_load(microsynth)

synth <- vio_df %>% select(c(week,year,violations,sip)) %>% microsynth(idvar="week", timevar="year", intvar="sip")

```
I can't get microsynth to work, but I also realized that we will need data from other states/counties in order to make it work. I looked for data, but I cant find anything current and useful, so a synthetic control is definitely out.